---
output:
  html_document:
    code_folding: hide
urlcolor: blue
---
```{r child = 'Knitr_setup.Rmd'}
```
```{r}
library(tidyr)
library(dplyr)
library(knitr)
library(stringr)
```

# Data preparation

The Steam Games Dataset was downloaded from [Kaggle](https://www.kaggle.com/datasets/fronkongames/steam-games-dataset) and contains 76987 games.

First, let's load the data and remove unnecessary columns to reduce the size of the data set. We will also convert the release date to a suitable date format and convert some columns from string to boolean. Also, the esimtated owner ranges are split into min and max values, and the mean is computed. Finally, we compute the estimated revenue for each game by multiplying the mean number of owners with the price. These are rough estimates, since Valve does not publish the exact number of owners for each game.

```{r}
games <- reasetd.csv('data/games.csv')

# Remove unnecessary columns
games <- games %>% select(
    -c(About.the.game, Reviews, Header.image, Full.audio.languages, Developers,
       Website, Support.url, Support.email, Metacritic.url, Notes, Screenshots, Movies))

# Convert release date to date format
games$Release.date <- as.Date(games$Release.date, format="%b %d, %Y")

# Convert booleans to 1 and 0 which is easier to handle for modelling
games$Windows <- ifelse(games$Windows == "True", 1, 0)
games$Mac <- ifelse(games$Mac == "True", 1, 0)
games$Linux <- ifelse(games$Linux == "True", 1, 0)

# Split the 'Estimated.owners' column into min and max values
owners.split <- strsplit(games$Estimated.owners, " - ")
games$Owners.min <- sapply(owners.split, function(x) as.numeric(x[1]))
games$Owners.max <- sapply(owners.split, function(x) as.numeric(x[2]))

# Compute the mean of the min and max values
games$Owners.mean <- rowMeans(cbind(games$Owners.min, games$Owners.max))

# Remove the original column
games <- select(games, -Estimated.owners)

# Compute the estimated revenue for each game
games$Revenue <- games$Owners.mean * games$Price

# Add log-transforms for extremely right-skewed variables
# Revenue is extremely right-skewed, so we will use the log of revenue instead
games <- games %>%
    mutate(Revenue.log = ifelse(Revenue > 0, log(Revenue), NA)) %>%
    mutate(Peak.CCU.log = ifelse(Peak.CCU > 0, log(Peak.CCU), NA)) %>%
    mutate(Positive.log = ifelse(Positive > 0, log(Positive), NA)) %>%
    mutate(Negative.log = ifelse(Negative > 0, log(Negative), NA))
```
After some cleanup, the data looks like this (only a small subset of variables is shown):

```{r}
kable(head(games %>% select(c(AppID, Name, Release.date, Price, Metacritic.score)), 5))
```

From the data given, we also compute additional variables that might be useful for our analysis, such as the number of supported languages.

```{r}
# Count the number of languages
games$Lang.count <- str_count(games$Supported.languages, ",") + 1

# Adjusting for empty brackets
games$Lang.count[games$Supported.languages == "[]"] <- 0

# Check for specific language support of the most common languages
games$Lang.English <- as.integer(sapply(games$Supported.languages, function(x) grepl("English", x)))
games$Lang.Spanish <- as.integer(sapply(games$Supported.languages, function(x) grepl("Spanish", x)))
games$Lang.Chinese <- as.integer(sapply(games$Supported.languages, function(x) grepl("Chinese", x)))
games$Lang.Russian <- as.integer(sapply(games$Supported.languages, function(x) grepl("Russian", x)))
games$Lang.German <- as.integer(sapply(games$Supported.languages, function(x) grepl("German", x)))
games$Lang.Portuguese <- as.integer(sapply(games$Supported.languages, function(x) grepl("Portuguese", x)))
games$Lang.French <- as.integer(sapply(games$Supported.languages, function(x) grepl("French", x)))
games$Lang.Italian <- as.integer(sapply(games$Supported.languages, function(x) grepl("Italian", x)))

# Remove the original column
games <- select(games, -Supported.languages)
```
Some numeric columns contain 0 instead of NA values, which we will replace with NA. Otherwise, the mean of these columns would be biased. This is somewhat poorly documented, but hints can be found in the code and the discussion section of the [Kaggle Data Card](https://www.kaggle.com/datasets/fronkongames/steam-games-dataset/data).

```{r}
for (col in c("Peak.CCU", "Metacritic.score", "User.score", "Positive", "Negative",
              "Average.playtime.forever", "Average.playtime.two.weeks",
              "Median.playtime.forever", "Median.playtime.two.weeks")) {
    # Replace 0 with NA in the specified column
    games[[col]][games[[col]] == 0] <- NA
}
```

A few publishers produce many games, while most publishers only produce a few games. We will create a new column that contains the number of games produced by each publisher. These are the top 3 publishers:

```{r}
games <- games %>%
    filter(Publishers != "") %>%
    group_by(Publishers) %>%
    mutate(Publishers.count = n()) %>%
    ungroup()

# Show the top publishers
publisher.counts <- sort(table(games$Publishers), decreasing=TRUE)
kable(head(publisher.counts, 3))
```

We will also create dummy variables for the top 10 genres and categories (shown below are the top 3). The tags are somewhat redundant with the genres, so we will not use them.

```{r}
# Split the 'Genres' column into individual genres and count them
genre.counts <- games %>%
    filter(Genres != "") %>%
    separate_rows(Genres, sep = ",") %>%
    count(Genres, name = "Count") %>%
    arrange(desc(Count))

top.genres <- head(genre.counts, 10)

# For each of the top genres, create a dummy variable
for(genre in head(top.genres$Genres)) {
    games[[paste0("Genre.", genre)]] <- as.integer(grepl(genre, games$Genres))
}

kable(head(top.genres, 3))
```

```{r}
category.counts <- games %>%
    filter(Categories != "") %>%
    separate_rows(Categories, sep = ",") %>%
    count(Categories, name = "Count")  %>%
    arrange(desc(Count))

top.categories <- head(category.counts, 10)

# For each of the top genres, create a dummy variable
for(category in top.categories$Categories) {
    games[[paste0("Category.", category)]] <- as.integer(grepl(category, games$Categories))
}

kable(head(top.categories, 3))
```

```{r include = FALSE }
# The tags are somewhat redundant with the genres, so we will not use them for now.
tag.counts <- games %>%
    filter(Tags != "") %>%
    separate_rows(Tags, sep = ",") %>%
    count(Tags, name = "Count")  %>%
    arrange(desc(Count))

head(tag.counts, 20)
```




Finally, we store the cleaned and enriched data set for further analysis.

```{r}
write.csv(games, 'data/games_clean.csv', row.names = FALSE)
```

```{r include = FALSE}
summary(games)
```
