---
output:
  html_document:
    code_folding: hide
urlcolor: blue
---
```{r child = 'Knitr_setup.Rmd'}
```
```{r}
library(dplyr)
library(knitr)
library(stringr)
```

# Data preparation

First, let's load the data and remove unnecessary columns to reduce the size of the data set. We will also convert the release date to a suitable date format and convert some columns from string to boolean.

```{r}
games <- read.csv('data/games.csv')
# Remove unnecessary columns
games <- games %>% select(
    -c(Estimated.owners, About.the.game, Reviews, Header.image, Full.audio.languages,
       Website, Support.url, Support.email, Metacritic.url, Notes, Screenshots, Movies))

# Convert release date to date format
games$Release.date <- as.Date(games$Release.date, format="%b %d, %Y")

# Convert booleans to 1 and 0 which is easier to handle for modelling
games$Windows <- ifelse(games$Windows == "True", 1, 0)
games$Mac <- ifelse(games$Mac == "True", 1, 0)
games$Linux <- ifelse(games$Linux == "True", 1, 0)
```

After some cleanup, the data looks like this (only a small subset of variables is shown):

```{r}
kable(head(games %>% select(c(AppID, Name, Release.date, Price, Metacritic.score)), 5))
```

From the data given, we also compute additional variables that might be useful for our analysis, such as the number of supported languages.

```{r}
# Count the number of languages
games$Lang.count <- str_count(games$Supported.languages, ",") + 1

# Adjusting for empty brackets
games$Lang.count[games$Supported.languages == "[]"] <- 0

# Check for specific language support of the most common languages
games$Lang.English <- as.integer(sapply(games$Supported.languages, function(x) grepl("English", x)))
games$Lang.Spanish <- as.integer(sapply(games$Supported.languages, function(x) grepl("Spanish", x)))
games$Lang.Chinese <- as.integer(sapply(games$Supported.languages, function(x) grepl("Chinese", x)))
games$Lang.Russian <- as.integer(sapply(games$Supported.languages, function(x) grepl("Russian", x)))
games$Lang.German <- as.integer(sapply(games$Supported.languages, function(x) grepl("German", x)))
games$Lang.Portuguese <- as.integer(sapply(games$Supported.languages, function(x) grepl("Portuguese", x)))
games$Lang.French <- as.integer(sapply(games$Supported.languages, function(x) grepl("French", x)))
games$Lang.Italian <- as.integer(sapply(games$Supported.languages, function(x) grepl("Italian", x)))

# Remove the original column
games <- select(games, -Supported.languages)
```

Finally, we store the cleaned and enriched data set for further analysis.

```{r}
write.csv(games, 'data/games_clean.csv', row.names = FALSE)
```

```{r include = FALSE}
summary(games)
```

#((Kommentare MJ))
- Datum in ein Date format für R umwandeln
- Genres aufteilen von einer Liste in individuelle (dummy)variablen
- Developers sind zu viele Daten für lineare Modelle, kann man diese gruppieren nach Grösse oder Region?
