---
output:
  html_document:
    code_folding: hide
urlcolor: blue
---

```{r child = 'Knitr_setup.Rmd'}
```
```{r}
library(knitr)
library(dplyr)
```
# Exploratory data analysis (EDA)

Before we dive into data analysis, we need to do some exploratory data analysis (EDA) to get a sense of what the data look like. This will help us to understand the data and to identify any potential problems with the data.

```{r}
column.classes <- c(Release.date = "Date")
games <- read.csv('data/games_clean.csv', colClasses = column.classes)
```

## Distribution of key variables

The game revenue distribution is extremely right skewed. This is not surprising as most games do not make much money, but a few games generate massive revenue. We therefore need to log-transform the revenue variable to make the distribution more symmetric, although we still see some right-skewness.

```{r}
mfrow <- par(mfrow = c(1, 2))
hist(games$Revenue.log, main = "Distribution of revenue", xlab = "Log revenue $")
boxplot(games$Revenue.log, main = "Distribution of revenue", ylab = "Log revenue $")
```
```{r include = FALSE}
# Show extreme right-skewness of revenue distribution
summary(games[games$Revenue > 0, c("Revenue", "Revenue.log")])
```



