---
output:
  html_document:
    code_folding: hide
urlcolor: blue
---

```{r child = 'Knitr_setup.Rmd'}
```

# Generalized linear model (GLM)

Generalized Linear Models (GLMs) are statistical models that can be used to predict the relationship between a response variable and one or more predictor variables. When analyzing our video game data, GLMs can be used to predict the relationship between a game's success and various factors such as the game's genre, platform, and critical reception. 

Suppose we are interested in predicting which factors influence a given game's chances of receiving a good user rating. In this case, we could consider the user score as our response variable and we would look at data such as price, popularity and genre as our predictor variables.

GLMs are useful because they can handle a wide range of data, including binary, count, and continuous data. Here are some examples of each type of data:

- Binary data:      Values such as "True" / "False" or 1/0. An example for binary data would be if a certain language supported or not.
- Count data:       Integer values (0,1,2,3...) that represent a number of occurrences of something. An example for count data would be the amount of DLCs a game has
- Continuous data:  Any value within a given range. An example for continuous data would be the amount of time a person has spent playing a certain game



## Poisson

The Poisson model is a type of GLM that is used to analyze count data. It can be particularly useful when we expect our response variable not follow a normal distribution or if we suspect non-linear relationships with the predictor variables. Since we can't rely on our data being normally distributed and all relationships being linear, it may make sense to explore the data using a Poisson model.

Some interesting count data we can look at in our data set is: 

- Peak concurrent users: Which factors contribute to a high peak of concurrent users?
- DLC count: DLC - downloadable content represents extra content in form of new missions, maps or items, usually released after the game has launched. We can try and find out which types of games tend to have more DLC.



((Prose))
((Filter games metacritic score, only look at games that have a metacritic score))
((use crossvalidation))

To fit a Poisson Model in R we will use the glm() function, where we can specify the distribution to be used with family = "poisson".

### DLC

Let us first take a look at what influences the DLC.count variable. We want to look at which variables lead to higher amounts of DLC. In recent years DLC has come under fire, for developers being lazy, trying to perform cash grabs by withholding content on release in order to release it as DLC later down the road.

```{r}

column.classes <- c(Release.date = "Date")
games.clean <- read.csv('data/games_clean.csv', colClasses = column.classes)


#release date crashes the model, because it must first be converted, however is it count data?
dlc.model1 <- glm(DLC.count ~ Price + Metacritic.score + Release.date + Positive + Negative, family = "poisson", data = games.clean)
summary(dlc.model1)


```
Interpreting the summary is not straightforward ((...why...))
However we can see that an increase in the DLC count variable is correlated to less positive reviews, hinting at our assumption from earlier that games with more DLC are rated worse.


((boxplot to see if data is even poisson))

Next we will try and look at what variables could influence the peak concurrent users (Peak CCU).
This is a metric 

```{r}
ccu.model2 <- glm(Peak.CCU ~  Price + Metacritic.score + Average.playtime.two.weeks, family = "poisson", data = games.clean)
summary(ccu.model2)
```



## Binomial

This dataset contains a few interesting areas to apply a binomial model.
PC games are usually developed for Windows, with Mac and Linux operating systems considered second rate.

Let us look at what predictors could be relevant to see if a game supports Linux or not.
Applying the following binomial logistic regression 

```{r}
#data preparation for binomial model


# 2. convert release date to numeric value for the model

ref.date <- as.Date("2000-01-01")
games.clean$Release.date <- as.numeric(games.clean$Release.date - ref.date)
```



```{r}

#model >> developers is too much data
linux.model3 <- glm(Linux ~ Release.date + Metacritic.score + Price, family = "binomial", data = games.clean)
summary(linux.model3)
```


