---
output:
  html_document:
    code_folding: hide
  pdf_document: default
urlcolor: blue
---

```{r child = 'Knitr_setup.Rmd'}
```

```{r data prep, Include = FALSE}
# Loading the data set
games <- read.csv('data/games_clean.csv')
```



# Linear model

A Linear Model is a statistical method used to model the relationship between a dependent (target) variable and one or more independent variables. The basic idea of a linear model is to represent the dependent variable as a linear combination of the independent variables. Linear models can be extended to consider multiple independent variables and then it is called multiple linear model.

A linear regression model typically utilizes count and continuous data. For binary data, more suitable models are available. Below, the data types are briefly described:

- Binary Data: Consists of values such as 'True' / 'False' or '1' / '0'. An example of binary data is whether a certain programming language is supported or not.<br>
- Count Data: Comprises integer values (0, 1, 2, 3, ...) that represent the number of occurrences of something. For instance, the number of downloadable content (DLC) packs a game has can be categorized as count data.<br>
- Continuous Data: Encompasses any value within a given range. An example of continuous data is the amount of time a person has spent playing a particular game.<br>
 
Certain questions can be examined using a linear model, for example:

- Which factors influence the Peak Concurrent Users (CCU) of games on Steam? <br>
- Which factors contribute to the financial success of a game, as measured by its revenue? <br>

## Peak Concurrent Users (CCU) 

Peak Concurrent Users (CCU) is a critical metric for gauging a game's popularity, reflecting the highest number of players online at the same time. It's an essential indicator for assessing a game's appeal and success. Understanding CCU helps identify what drives player engagement in the competitive gaming landscape.<br>

### Simple Model

We start with a simple model taking only one predictor, which is the variable Revenue.log. We want to predict if the Peak CCU increases with higher revenue.  

```{r simple lm ccu}
df <- games[, c("Peak.CCU.log", "Revenue.log")]

# Creating a simple linear model
simple_model <- lm(Peak.CCU.log ~ Revenue.log, data = df)

# Plot
plot(df$Revenue.log, df$Peak.CCU.log, pch = 20,
     xlab = "Revenue.log", ylab = "Peak.CCU.log")

# Regression line
abline(simple_model, col = 'red', lwd = 2)  
```

The scatter plot reveals a positive correlation between Revenue.log and Peak.CCU.log, as indicated by the upward slope of the regression line. However, the widespread dispersion of data points suggests variability that extends beyond what is explained by revenue alone.

```{r simple lm ccu summary}
summary(simple_model)
```
In the linear model, the intercept value of around -6.38 suggests that if the Revenue.log were zero, which is impossible as the logarithm of zero is undefined, the expected Peak.CCU.log would be -6.38. The slope coefficient of 0.65 indicates that for each unit increase in Revenue.log, there is an average increase of 0.65 units in Peak.CCU.log. Even though there is strong evidence that Revenue.log might have an impact on the Peak.CCU.log. The R-squared value is only of approximately 0.391, implying that other factors influencing user numbers remain unaccounted for.

Therefore, we modify our linear model by including additional predictors to enhance the R-squared value. However, we are losing more observations, since some of the variables are not available for all games.


```{r lm ccu}
# Creating a linear model for Peak Concurrent Users (CCU)
model <- lm(Peak.CCU.log ~ Owners.mean + Metacritic.score + Positive.log + 
              Publishers.count + Category.PvP + Recommendations +
              Revenue.log, data = games)

# Displaying the model summary
summary(model)

```
### Interpretation

This linear regression analysis reveals key factors driving the popularity of video games, as indicated by peak concurrent users. Notably, the model highlights several significant predictors of a game's success. High Metacritic scores, positive user reviews, a diverse range of publishers, player versus player (PvP) features, and strong recommendations are all positively correlated with higher peak concurrent users. Interestingly, more widely owned games show a slight negative impact on peak CCU, possibly reflecting market saturation.

From an investment perspective, the analysis underscores the importance of critical acclaim, positive user reception, and PvP elements in driving a game's popularity. The strong statistical significance of these factors suggests they are reliable indicators of a game's potential success. With about 70% of the variance in peak CCU explained by these variables, investors can make more informed decisions on which games or gaming companies to back. This model offers a valuable tool for understanding the dynamics of the gaming market and identifying promising investment opportunities.


## Revenue

Revenue, indicating a game's financial success, hinges on factors like price and sales volume. Higher-priced games can earn more, but the number of players buying the game is crucial. DLC (Downloadable Content) enhances appeal and can boost sales. Positive reviews and player recommendations also increase popularity and revenue. Understanding these dynamics is key for game developers and investors in the gaming market.<br>

Let's use a linear model to explain revenue based on the following variables: number of owners (Owners.mean), peak concurrent users (Peak.CCU.log), critical acclaim (Metacritic.score), user feedback (Positive.log, Negative.log), and publisher size (Publishers.count).

```{r lm revenue} 
# Creating a linear model for Revenue
model_revenue <- lm(Revenue.log ~  Owners.mean + Peak.CCU.log +
                      Metacritic.score + Positive.log + Negative.log +
                      Publishers.count, data = games)

summary(model_revenue)

```

Key findings include the strong correlation between player engagement (measured by peak concurrent users) and game revenue, emphasizing the importance of investing in games that actively engage players. User feedback, both positive and negative, significantly impacts revenue, highlighting the value of games that generate active community discussion. Additionally, critical acclaim, indicated by Metacritic scores, is a vital factor in a game's profitability. The result also suggests that publishers with more games in the dataset tend to produce games with more revenue per game, although the evidence is rather weak. Overall, for investors, prioritizing games with high player engagement, active community interaction, critical acclaim, and broad distribution is a strategic approach to maximize returns in the gaming industry.


